Balance responses in MS

### 2020-02-04 R/msBalance.Rmd
updated plots of EMG magnitudes to show only the top 3 codes of each cell

## Data processing
Each individual EMG record was registered to the onset of treadmill motion and resampled to a common sample rate (1 kHz), and processed (high-pass, 35 Hz, de- mean, rectify, low-pass, 40 Hz) as in previous studies.[@lang2019; @mckay2016]
Recorded EMG records were visualized stratified by disease state and perturbation direction (`r figureNumbers("rawEmg", display = "cite")`).
By visual inspection, there were some gross magnitude differences in recorded EMG levels between the MS and control groups, with higher EMG levels overall in the MS group.
EMG levels were therefore normalized to the maximum values obtained in a 1 second window after perturbation onset after averaging across like trials (`r tableNumbers("emgMags", display = "cite")`).

@@

***
```{r rawEMG, out.width = "100%", fig.align = "left", fig.cap = captionRawEmg}
p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
  geom_jitter(mapping = aes(x = 0, y = Vm, color = Participant), data = taRNorm %>% left_join(participants %>% select(Participant, Group)), show.legend = FALSE, height = 0, width = 0.01)
p
```

>>>>

## Data processing
Each individual EMG record was registered to the onset of treadmill motion and resampled to a common sample rate (1 kHz), and processed (high-pass, 35 Hz, de- mean, rectify, low-pass, 40 Hz) as in previous studies.[@lang2019; @mckay2016]
Recorded EMG records were visualized stratified by disease state and perturbation direction (`r figureNumbers("rawEmg", display = "cite")`).

@@

***
```{r rawEMG, out.width = "100%", fig.align = "left", fig.cap = captionRawEmg}
# p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
#   geom_jitter(mapping = aes(x = 0, y = Vm, color = Participant), data = taRNorm %>% left_join(participants %>% select(Participant, Group)), show.legend = FALSE, height = 0, width = 0.01)
# p
# p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
#   geom_label(mapping = aes(x = 0, y = Vm, color = Participant, label = Participant), data = taRNorm, show.legend = FALSE)
# p
p = ggplot(taR, aes(x = Time, y = V)) +
  geom_line(color = "Gray90", show.legend = FALSE, alpha = 0.5) +
  geom_line(aes(color = Participant), taRAv, show.legend = FALSE, alpha = 0.5) +
  facet_grid(Group ~ `Perturbation Direction`) +
  theme_minimal_grid() +
  geom_text(mapping = aes(x = 0, y = Vm, color = Participant, label = Participant), data = taRNorm %>% group_by(Group, `Perturbation Direction`) %>% top_n(3), show.legend = FALSE)
p
```

By visual inspection, there were some gross magnitude differences in recorded EMG levels between the MS and control groups, with higher EMG levels overall in the MS group.
EMG levels in most control participants (with the exception of MSC15 and MSC18) were generally roughly an order of magnitude lower than levels in MS participants.
This number is difficult to interpret, as it can reflect a large number of biological and methodological factors, so that increased absolute level among MS could reflect increased muscle activation or completely unrelated factors.
EMG levels were therefore normalized to the maximum values obtained in a 1 second window after perturbation onset after averaging across like trials (`r tableNumbers("emgMags", display = "cite")`).
